PInSoRo: A Dataset for Deep-Learning of Human-Robot Social Interactions

### 2017-06-28 paper.tex
Added a link to the temporary website

The dataset is freely available to any interested researcher\footnote{Note to
the reviewers: the link to the dataset's dedicated website will be added to the
final version of the article.}. Due to ethical and data protection regulations,
the dataset is however made available in two forms: a public, Creative-Commons
licensed, version that do not include any video material of the children (no
video streams, audio included); and a complete version that includes all video
streams. This second version is freely available as well, but interested
researchers must first fill a data protection form.

>>>>

The dataset is freely available to any interested researcher\footnote{Note to
the reviewers: for the purpose of the review, an excerpt of the dataset is
available online: \url{https://freeplay-sandbox.github.io/}. A link to the
complete dataset will be made available in the final version of the article.}.
Due to ethical and data protection regulations, the dataset is however made
available in two forms: a public, Creative-Commons licensed, version that do
not include any video material of the children (no video streams, audio
included); and a complete version that includes all video streams. This second
version is freely available as well, but interested researchers must first fill
a data protection form.
